Supplemental material

### 2024-08-22 paper/supp_material.tex
final version

\usepackage{stmaryrd}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{animate, dsfont, here, xspace}
%\usepackage{tikz}
\usepackage{tikz,pgfplots}
 \pgfplotsset{compat=1.17}
%\includepdf[fitpaper=true, pages=-]{img/pdg.pdf}

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\Determinant}{det}
\renewcommand{\P}{\mathds{P}} %Apparement \P existe déjà ?
\newcommand\N{\mathds{N}}
\newcommand\Norm{\mathcal{N}}
\newcommand\R{\mathds{R}}
\newcommand\Z{\mathds{Z}}
\newcommand{\determinant}[1]{\Determinant\left(#1\right)}
%\newcommand\C{\mathds{C}}
%\newcommand\Z{\mathds{Z}}

@@

%\DefineBibliographyStrings{english}{andothers={et\addabbrvspace alii}}
\usepackage[authordate16,backend=biber,maxcitenames=2]{biblatex-chicago}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{biblatex}
\addbibresource{biblio.bib}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Improving real-time trend estimates using local parametrisation of local polynomial regression filters},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Improving real-time trend estimates using local parametrisation
of local polynomial regression filters}
\author{}
\date{}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden]}{\end{tcolorbox}}\fi

\setstretch{2}
\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

This paper studies and compares real-time estimates of the trend cycle
component with moving averages based on local polynomial regression. In
particular, this theory allows to reproduce Henderson's symmetric and
Musgrave's asymmetric filters. This paper describes how they can be
extended to include a timeliness criterion to minimise the phase shift.
While asymmetric filters are generally parameterised globally, which can
be suboptimal around turning points, this paper proposes a procedure for
parameterising them locally. An empirical comparison, based on simulated
and real data, shows that modelling polynomial trends that are too
complex introduces more revisions without reducing the phase shift, and
that local parameterisation reduces the delay in detecting turning
points and reduces revisions. The paper also shows how these results can
be easily reproduced using the R package \texttt{rjd3filters} dedicated
to the manipulation of moving averages.

Keywords: time series, trend-cycle, seasonal adjustment, turning points,
R statistical software.

JEL Classification: E32, E37.

\hypertarget{introduction}{%
\section*{Introduction}\label{introduction}}
\addcontentsline{toc}{section}{Introduction}

Analysis of the economic cycle, and in particular the early detection of
turning points in a series, is a major topic in the analysis of economic
outlook. To this end, economic indicators are generally seasonally
adjusted. However, in order to improve their interpretability, it may be
necessary to perform additional smoothing in order to reduce noise, and
thus analyse the trend-cycle component. By construction, trend-cycle
extraction methods are closely related to seasonal adjustment methods,
since they are generally applied to seasonally adjusted series.

A moving average, or linear filter, is a statistical method that
consists in applying a rolling weighted mean to a times series: for each
date \(t\) it computes a weighted mean of \(p\) past points and \(q\)
future points where \(p,q\geq0\) depends on the moving average. Moving
averages are ubiquitous in business cycle extraction and seasonal
adjustment methods. For example, the X-13ARIMA seasonal adjustment
method uses several moving averages to estimate the main components of a
time series. Symmetric filters are applied to the center of the series,
but when it comes to estimate the most recent points, all of these
methods must rely on asymmetric filters. For trend-cycle extraction, the
most popular symmetric filter is the \textcite{henderson1916note} moving
average, which is used in the X-13ARIMA seasonal adjustment algorithm.

However, for real-time estimates, due to the lack of future
observations, all these methods must rely on asymmetric filters to
estimate the most recent points. For example, for trend-cycle
extraction, X-13ARIMA uses Henderson's symmetric filter and
\textcite{musgrave1964set}'s asymmetric filters on an extended series
using an ARIMA model. Since the predicted values are linear combinations
of past values, this amounts to applying asymmetric averages at the end
of the series.

If the classic asymmetric moving averages have good properties regarding
the future revisions induced by the process (see for example
\textcite{pierce1980SA}), they create, by construction, phase shifts
that impact the real-time estimation of turning points, introducing time
delay in the detection.

Using local polynomial regression, \textcite{proietti2008} developed
general class of symmetric and asymmetric moving averages. In
particular, it makes possible to reproduce Henderson's symmetric filter
and Musgrave's asymmetric filters. However, these methods have two
drawbacks. Firstly, the phase shift (i.e.~the delay in detecting turning
points) is not directly controlled. Secondly, asymmetric filters depend
on a parameter that is generally estimated over the whole series using
assumptions that may be wrong locally. The aim of this study is to
propose extensions to the \textcite{proietti2008} class of filters in
order to take these shortcomings into account. The extensions have been
implemented in the \faIcon{r-project} \texttt{rjd3filters} package
(available at \url{https://github.com/rjdemetra/rjd3filters}) and are
therefore easily reusable.

In Section~\ref{sec-propMM}, we describe the general properties of
moving averages and the associated quality criteria. This allows us to
understand the foundations behind the construction of moving averages
from local polynomial regressions, as well as those behind the two
extensions proposed in this article (Section~\ref{sec-nonparamreg}). In
a final section (Section~\ref{sec-comparison}), all these methods are
compared empirically on simulated and real series.

\hypertarget{sec-propMM}{%
\section{Some properties on moving averages}\label{sec-propMM}}

Lots of papers describe the definition and the properties of moving
averages and linear filters, see for example \textcite{ch12HBSA}. In
this section we summarize some of the main results to understand the
next sections.

Let \(p\) et \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) or \(M\) is defined by a set of coefficients
\(\boldsymbol\theta=\begin{pmatrix}\theta_{-p}\\\vdots\\\theta_{f}\end{pmatrix}\)
such as for all time series \(X_t\): \[
M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

\begin{itemize}
\item
  \(p+f+1\) is called the \emph{moving average order}.
\item
  When \(p=f\) the moving average is said to be \emph{centered}. If we
  also have \(\forall k:\:\theta_{-k} = \theta_k\), the moving average
  \(M_{\boldsymbol\theta}\) is said to be \emph{symmetric}. In this
  case, the quantity \(h=p=f\) is called the \emph{bandwidth}.
\end{itemize}

\hypertarget{subsec:gain-deph}{%
\subsection{Gain and phase shift functions}\label{subsec:gain-deph}}

To interpret the notions of gain and phase shift, it is useful to
illustrate the effects of moving averages on harmonic series
\(X_t=\e^{-i\omega t}\) with \(\omega\in[0,\pi]\). The moving average
\(M_{\boldsymbol\theta}\) transforms \(X_t\) into: \[
Y_t = M_{\boldsymbol\theta}X_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot X_t.
\] The function
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}\)
is called the \emph{transfer function} or \emph{frequency response
function}. The frequency response function can equivalently be defined
as
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}\)
ou
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}\).
It can be rewritten as: \[
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
\] where
\(\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert\)
is the \emph{gain} or \emph{amplitude} function and
\(\varphi_{\boldsymbol\theta}(\omega)\) is the \emph{phase shift} or
\emph{time shift} function. This function is sometimes represented as
\(\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}\)
to mesure the phase shift in number of periods. For all symmetric moving
average we have
\(\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})\).

To sum up, applying a moving average to a harmonic times series
(\(X_t=\e^{-i\omega t}\)) affects it in in two different ways:

\begin{itemize}
\item
  by multiplying it by an amplitude coefficient
  \(\rho_{\boldsymbol\theta}\left(\omega\right)\) (gain);
\item
  by ``shifting'' it in time by
  \(\varphi_{\boldsymbol\theta}(\omega)/\omega\) which directly affects
  the detection of turning points. When
  \(\varphi_{\boldsymbol\theta}(\omega)/\omega<0\) the time shift is
  negative: the turning point is detected with delay.
\end{itemize}

Fourier decomposition allows to analyze any time series as a sum of
harmonic series, and each component (trend, cycle, seasonal, irregular)
is associated with a set of frequencies. Noting \(\omega = 2\pi/p\), the
harmonic series of frequency \(\omega\) represents a series that repeats
itself every \(p\) periods. For example, for a monthly series (12
observations per year), seasonal movements are those that repeat every
year: they are therefore associated with frequencies \(2\pi/12\) (annual
periodicity), \(2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5\). In this
paper, we consider that the trend-cycle is associated with frequencies
in the interval \([0, 2\pi/12[\), i.e.~movements recurring at least
every 12 months. Even if different frequencies are sometimes used
(e.g.~\([0, 2\pi/36]\) to consider only cycles of at least 36 months),
this has no impact on the results of the study. The other frequencies,
\([2\pi/12, \pi]\) are associated with the irregular component
(undesirable oscillations).

Figure~\ref{fig-graphsmusgrave} shows the gain and phase shift function
for the asymmetric Musgrave filter (see Section~\ref{sec-lppasymf})
often used for real-time trend-cycle estimation (i.e.~when no point in
the future is known). The gain function is greater than 1 on the
frequencies associated with the trend-cycle (\([0, 2\pi/12]\)): this
means that the trend-cycle is well preserved and that short cycles of 1
to 2 years (\([2\pi/24,2\pi/12]\)) are even amplified. However, cycles
of 8 to 12 months (\([2\pi/12, 2\pi/8]\)), considered undesirable
because associated with the irregular, are also amplified: this can lead
to the detection of false turning points. At other frequencies, the gain
function is less than 1, but always positive: this means that the series
smoothed by this moving average will always contain noise, even if it is
attenuated. Analysis of the phase shift shows that the shorter the
cycles, the greater the phase shift: this means that on series smoothed
by this moving average, turning points could be detected at the wrong
date.

\begin{figure}[H]

\caption{\label{fig-graphsmusgrave}Coefficients, gain and phase shift
function for the Musgrave filter in real time with \(I/C=3.5\).}

{\centering \includegraphics[width=1\textwidth,height=\textheight]{img/filters_used/musgrave.pdf}

@@

\end{figure}

\hypertarget{desirable-properties-of-a-moving-average}{%
\subsection{Desirable properties of a moving
average}\label{desirable-properties-of-a-moving-average}}

To decompose a time series into a seasonal component, a trend-cycle and
the irregular, the X-11 decomposition algorithm (used in X-13ARIMA) uses
a succession of moving averages, all with specific constraints.

In our case, we assume that our initial series \(y_t\) is seasonally
adjusted and can be written as the sum of a trend-cycle, \(TC_t\), and
an irregular component, \(I_t\): \[
y_t=TC_t+I_t.
\] The aim will be to build moving averages that best preserve the
trend-cycle (\(M_{\boldsymbol\theta} (TC_t)\simeq TC_t\)) and minimise
noise (\(M_{\boldsymbol\theta} (I_t)\simeq 0\)).

\hypertarget{trend-preservation}{%
\subsubsection{Trend preservation}\label{trend-preservation}}

Trend-cycles are generally modelled by local polynomial trends (see
Section~\ref{sec-nonparamreg}). In order to best preserve the
trend-cycles, we try to have moving averages that preserve the
polynomial trends. A moving average \(M_{\boldsymbol\theta}\) preserves
a function of time \(f(t)\) if
\(\forall t:M_{\boldsymbol\theta} f(t)=f(t)\).

We have the following properties for the moving average
\(M_{\boldsymbol\theta}\):

\begin{itemize}
\item
  To preserve a constant trend \(X_t=a\) we need: \[
  \forall t:M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}=\sum_{k=-p}^{+f}\theta_ka=a\sum_{k=-p}^{+f}\theta_k=a.
  \] The sum of the coefficients of the moving average
  \(\sum_{k=-p}^{+f}\theta_k\) must then be equal to \(1\).
\item
  To preserve linear trends \(X_t=at+b\) we need: \[
  \forall t:\:M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}=\sum_{k=-p}^{+f}\theta_k[a(t+k)+b]=a\sum_{k=-p}^{+f}k\theta_k+(at+b)\sum_{k=-p}^{+f}\theta_k=at+b.
  \] Which is equivalent to: \[
  \sum_{k=-p}^{+f}\theta_k=1
  \quad\text{et}\quad
  \sum_{k=-p}^{+f}k\theta_k=0.
  \]
\item
  In general, \(M_{\boldsymbol\theta}\) preserves polynomials of degree
  \(d\) if and only if: \[
  \sum_{k=-p}^{+f}\theta_k=1
   \text{ and }
  \forall j \in \left\llbracket 1,d\right\rrbracket:\:
  \sum_{k=-p}^{+f}k^j\theta_k=0.
  \]
\item
  If \(M_{\boldsymbol\theta}\) is symmetric (\(p=f\) and
  \(\theta_{-k} = \theta_k\)) and preserves polynomials of degree \(2d\)
  then it also preserves polynomials of degree \(2d+1\).
\end{itemize}

\hypertarget{noise-reduction}{%
\subsubsection{Noise reduction}\label{noise-reduction}}

All time series are affected by noise, which can blur the extraction of
trends and cycles. This is why we try to reduce this noise (by reducing
its variance) while preserving the relevant trends. The sum of the
squares of the coefficients \(\sum_{k=-p}^{+f}\theta_k^2\) is the
\emph{reduction of variance} ratio.

Indeed, let \(\{\varepsilon_t\}\) a sequence of independent random
variables with \(\E{\varepsilon_t}=0\), \(\V{\varepsilon_t}=\sigma^2\):
\[
\V{M_{\boldsymbol\theta}\varepsilon_t}=\V{\sum_{k=-p}^{+f} \theta_k \varepsilon_{t+k}}
= \sum_{k=-p}^{+f} \theta_k^2 \V{\varepsilon_{t+k}}=
\sigma^2\sum_{k=-p}^{+f} \theta_k^2.
\]

\hypertarget{sec-mmasym}{%
\subsection{Real-time estimation and asymmetric moving
average}\label{sec-mmasym}}

\hypertarget{sec-mmetprev}{%
\subsubsection{Asymmetric moving averages and
forecasts}\label{sec-mmetprev}}

For symmetric filters, the phase shift function is equal to zero (modulo
\(\pi\)). So there is no delay in detecting turning points. However,
they cannot be used in the beginning and in the end of the time series
because no past or future value can be used. Thus, for real-time
estimation, it is needed to build asymmetric moving average that
approximate the symmetric moving average.

Several approaches can be used for real-time estimation:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Use asymmetric moving averages to take account of the lack of
  available data;
\item
  Apply symmetrical filters to extended forecast series. This method
  seems to date back to \textcite{deforest1877adjustment}, which also
  suggests modelling a polynomial trend of degree three or less at the
  end of the period:\\
  ``\emph{As the first \(m\) and last \(m\) terms of the series cannot
  be reached directly by the formula, the series should be graphically
  extended by m terms at both ends, first plotting the observations on
  paper as ordinates, and then extending the curve along what seems to
  be its probable course, and measuring the ordinates of the extended
  portions.} \emph{It is not necessary that this extension should
  coincide with what would be the true course of the curve in those
  parts. } \emph{The important point is that the m terms thus added,
  taken together with the \(m+1\) adjacent given terms, should follow a
  curve whose form is approximately algebraic and of a degree not higher
  than the third.}''\\
  This is also the approach used in the X-13ARIMA seasonal adjustment
  method, which extends which extends the series by one year with an
  ARIMA model.
\end{enumerate}

Ultimately, the second method is equivalent to using asymmetric moving
averages, since forecasts are linear combinations of the past.

Conversely, the implicit forecasts of an asymmetric moving average can
be deduced from a reference symmetric moving average. This allows to
judge the quality of real-time estimates of the trend-cycle and to
anticipate future revisions when forecasts are far from expected
evolutions.\\
Let us denote \(v=(v_{-h},\dots, v_{h})\) the reference symmetrical
moving average and \(w^0,\dots w^{h-1}\) a sequence of asymmetrical
moving averages, of order \(h+1\) to \(2h\) used to estimate the last
\(h\) points with, for convention, \(w_t^q=0\) for \(t>q\). This means
that \(w^0=(w_{-h}^0,\dots, w_{0}^0)\) is used for estimation in real
time (when no points are known in the future),
\(w^1=(w_{-h}^1,\dots, w_{1}^1)\) for estimation of the penultimate
point (when only one point is known in the future), and so on. Let also
note \(y_{-h},\dots,y_{0}\) the observed series studied and
\(y_{1}^*,\dots y_h^*\) the implicit forecast induced by
\(w^0,\dots w^{h-1}\). This means that for all \(q\) we have: \[
\forall q, \quad \underbrace{\sum_{i=-h}^0 v_iy_i + \sum_{i=1}^h v_iy_i^*}_{\text{smoothing by }v\text{ of the extended series}}
=\underbrace{\sum_{i=-h}^0 w_i^qy_i + \sum_{i=1}^h w_i^qy_i^*}_{\text{smoothing by }w^q\text{ of the extended series}}.
\] This is equivalent to: \[
\forall q, \quad \sum_{i=1}^h (v_i- w_i^q) y_i^*
=\sum_{i=-h}^0 (w_i^q-v_i)y_i.
\] To sum up, in matrix form, this is equivalent to solving: \[
\scriptstyle
\begin{pmatrix}
  v_1 & v_2 & \cdots & v_h \\
  v_1 - w_1^1 & v_2 & \cdots & v_h \\
  \vdots & \vdots & \cdots & \vdots \\
   v_1 - w_1^{h-1} & v_2-w_2^{h-1} & \cdots & v_h
\end{pmatrix}
\begin{pmatrix}y_1^* \\ \vdots \\ y_h^*\end{pmatrix}=
\begin{pmatrix}
  w_{-h}^0 - v_{-h} & w_{-(h-1)}^0 - v_{-(h-1)} & \cdots & w_{0}^0 - v_{0} \\
  w_{-h}^1 - v_{-h} & w_{-(h-1)}^1 - v_{-(h-1)} & \cdots & w_{0}^1 - v_{0} \\
  \vdots & \vdots & \cdots & \vdots \\
  w_{-h}^{h-1} - v_{-h} & w_{-(h-1)}^{h-1} - v_{-(h-1)} & \cdots & w_{0}^{h-1} - v_{0}
\end{pmatrix}
\begin{pmatrix}y_{-h} \\ \vdots \\ y_0\end{pmatrix}.
\] This is implemented in the \texttt{rjd3filters::implicit\_forecast()}
function.

As highlighted by \textcite{wildischis2004}, extending the series
through forecasting with an ARIMA model is equivalent to calculating
asymmetric filters whose coefficients are optimised in relation to the
one-step ahead forecast. In other words, the aim is to minimise the
revisions between the first and last estimates (with the symmetric
filter). However, the phase shift induced by the asymmetric filters is
not controlled: we might prefer to have faster detection of turning
points and a larger revision rather than just minimising the revisions
between the first and last estimates. Furthermore, since the
coefficients of the symmetric filter (and therefore the weight
associated with distant forecasts) decrease slowly, we should also be
interested in the performance of multi-step ahead forecasting. This is
why it may be necessary to define alternative criteria for judging the
quality of asymmetric moving averages.

\hypertarget{subsec:crit-qual}{%
\subsubsection{Quality indicators for asymmetric moving
averages}\label{subsec:crit-qual}}

For asymmetric filters, most of the criteria come from those defined by
\textcite{ch15HBSA} and \textcite{trilemmaWMR2019} to build asymmetric
filters. They are summarised in Table~\ref{tab-QC} and can be calculated
using the \texttt{rjd3filters::diagnostic\_matrix()} function.

\textcite{ch15HBSA} propose a general approach to derive linear filters,
based on an optimisation problem involving three criteria:
\emph{Fidelity} (\(F_g\)), \emph{Smoothness} (\(S_g\)) and
\emph{Timeliness} (\(T_g\)). Fidelity can be directly linked to the
reduction in variance created by the filter, and timeliness to the
notion of phase shift, which again we want to be low. This method can be
used in\faIcon{r-project} with the function
\texttt{rjd3filters::fst\_filter()}.

\textcite{trilemmaWMR2019} propose an approach based on the
decomposition of the mean squared error between the symmetric and the
asymmetric filter in four quantities: \emph{Accuracy} (\(A_w\)),
\emph{Timeliness} (\(T_w\)), \emph{Smoothness} (\(S_w\)) and
\emph{Residual} (\(R_w\)). A simplified version of this method can be
used in \faIcon{r-project} with the function
\texttt{rjd3filters::dfa\_filter()}.

\begin{table}[!h]
\caption{\label{tab-QC} Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3,5$.}
{\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccc}
\toprule
Code & Description & Formula\\
\midrule
$b_c$ & Constant bias & $\sum_{k=-p}^{+f}\theta_{k}-1$\\
$b_l$ & Linear bias & $\sum_{k=-p}^{+f}k\theta_{k}$\\
$b_q$ & Quadratic bias & $\sum_{k=-p}^{+f}k^{2}\theta_{k}$\\
$F_g$ & Variance reduction / Fidelity (Guggemos) & $\sum_{k=-p}^{+f}\theta_{k}^{2}$\\
$S_g$ & Smoothness (Guggemos) & $\sum_{j}(\nabla^{3}\theta_{j})^{2}$\\
\addlinespace
$T_g$ & Timeliness (Guggemos) & $\int_{0}^{\omega_1}\rho_{\boldsymbol\theta}(\omega)\sin(\varphi_{\boldsymbol\theta}(\omega))^{2}\ud\omega$\\
$A_w$ & Accuracy (Wildi) & $2\int_0^{\omega_1}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$T_w$ & Timeliness (Wildi) & $8\int_0^{\omega_1} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
$S_w$ & Smoothness (Wildi) & $2\int_{\omega_1}^{\pi}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$R_w$ & Residual (Wildi) & $8\int_{\omega_1}^{\pi} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
\bottomrule
\end{tabular}}}

\textit{Note: $X_g$ criteria from Grun-Rehomme et al (2018) and $X_w$ criteria from Wildi and McElroy (2019).}

\textit{$\rho_s$ and $\varphi_s$ represent the gain and phase shift function of the symmetric Henderson filter.}

\textit{$h$ is the spectral density of the input series, considered to be that of white noise ($h_{WN}(x)=1$) or a random walk ($h_{RW}(x)=\frac{1}{2(1-\cos(x))}$).}
\end{table}

\hypertarget{sec-nonparamreg}{%
\section{Non-parametric regression and local polynomial
regression}\label{sec-nonparamreg}}

Many trend-cycle extraction methods are based on non-parametric
regressions, which are particularly flexible because they do not assume
any predetermined dependency in the predictors. In practice, local
regressions can be used. More specifically, consider a set of points
\((x_i,y_i)_{1\leq i\leq n}\). Non-parametric regression involves
assuming that there exists a function \(\mu\), to be estimated, such
that \(y_i=\mu(x_i)+\varepsilon_i\) with \(\varepsilon_i\) an error
term. According to Taylor's theorem, for any point \(x_0\), if \(\mu\)
is differentiable \(d\) times, then:
\begin{equation}\protect\hypertarget{eq-taylor}{}{
\forall x \::\:\mu(x) = \mu(x_0) + \mu'(x_0)(x-x_0)+\dots +
\frac{\mu^{(d)}(x_0)}{d!}(x-x_0)^d+R_d(x),
}\label{eq-taylor}\end{equation} where \(R_d\) is a negligible residual
term in the neighbourhood of \(x_0\). In a neighbourhood \(h(x_0)\)
around \(x_0\), \(\mu\) can be approximated by a polynomial of degree
\(d\). The quantity \(h(x_0)\) is called the \emph{bandwidth}. If
\(\varepsilon_i\) is white noise, then we can estimate by least squares
\(\mu(x_0)\) using the observations which are in
\(\left[x_0-h(x_0),x_0+h(x_0)\right]\).

In practice, this means assuming that the trend is locally polynomial.
Various estimation methods can be used to derive symmetrical and
asymmetrical moving averages.\\
\textcite{GrayThomson1996} propose a complete statistical framework
which makes it possible, in particular, to model the error in
approximating the trend by local polynomials. However, as the
specification of this error is generally complex, simpler models may be
preferred, such as that of \textcite{proietti2008}.\\
Finally, \textcite{dagumbianconcini2008} propose a similar modelling of
the trend-cycle but using the theory of Hilbert spaces with reproducing
kernels for estimation, which has the particular advantage of
facilitating the calculation of different moving averages at different
time frequencies. This method can be used in\faIcon{r-project} with the
function \texttt{rjd3filters::rkhs\_filter()}.

\hypertarget{symmetric-moving-averages-and-local-polynomial-regression}{%
\subsection{Symmetric moving averages and local polynomial
regression}\label{symmetric-moving-averages-and-local-polynomial-regression}}

Using \textcite{proietti2008}'s notation, we assume that our time series
\(y_t\) can be decomposed into \[
y_t=\mu_t+\varepsilon_t,
\] where \(\mu_t\) is the trend and
\(\varepsilon_{t}\overset{i.i.d}{\sim}\mathcal{N}(0,\sigma^{2})\) is the
noise (the series is therefore seasonally adjusted). Within a
neighbourhood \(h\) of \(t\), the local trend \(\mu_t\) is approximated
by a polynomial of degree \(d\), such that \(\mu_t\simeq m_{t}\) with:
\[
\forall j\in\left\llbracket -h,h\right\rrbracket:\:
y_{t+j}=m_{t+j}+\varepsilon_{t+j},\quad m_{t+j}=\sum_{i=0}^{d}\beta_{i}j^{i}.
\] The problem of trend extraction is equivalent to estimating
\(m_t=\beta_0\) (the constant in the previous formula).

In matrix notation: \[
\underbrace{\begin{pmatrix}y_{t-h}\\
y_{t-(h-1)}\\
\vdots\\
y_{t}\\
\vdots\\
y_{t+(h-1)}\\
y_{t+h}
\end{pmatrix}}_{\boldsymbol y}=\underbrace{\begin{pmatrix}1 & -h & h^{2} & \cdots & (-h)^{d}\\
1 & -(h-1) & (h-1)^{2} & \cdots & (-(h-1))^{d}\\
\vdots & \vdots & \vdots & \cdots & \vdots\\
1 & 0 & 0 & \cdots & 0\\
\vdots & \vdots & \vdots & \cdots & \vdots\\
1 & h-1 & (h-1)^{2} & \cdots & (h-1)^{d}\\
1 & h & h^{2} & \cdots & h^{d}
\end{pmatrix}}_{\boldsymbol X}\underbrace{\begin{pmatrix}\beta_{0}\\
\beta_{1}\\
\vdots\\
\vdots\\
\vdots\\
\vdots\\
\beta_{d}
\end{pmatrix}}_{\boldsymbol \beta}+\underbrace{\begin{pmatrix}\varepsilon_{t-h}\\
\varepsilon_{t-(h-1)}\\
\vdots\\
\varepsilon_{t}\\
\vdots\\
\varepsilon_{t+(h-1)}\\
\varepsilon_{t+h}
\end{pmatrix}}_{\boldsymbol \varepsilon}.
\]

>>>>

\usepackage{stmaryrd}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{animate, dsfont, here, xspace}
%\usepackage{tikz}
\usepackage{tikz,pgfplots}
 \pgfplotsset{compat=1.17}
%\includepdf[fitpaper=true, pages=-]{img/pdg.pdf}

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\Determinant}{det}
\renewcommand{\P}{\mathds{P}} %Apparement \P existe déjà ?
\newcommand\N{\mathds{N}}
\newcommand\Norm{\mathcal{N}}
\newcommand\R{\mathds{R}}
\newcommand\Z{\mathds{Z}}
\newcommand\transp[1]{{#1}^T}
%\newcommand\C{\mathds{C}}
%\newcommand\Z{\mathds{Z}}

@@

%\DefineBibliographyStrings{english}{andothers={et\addabbrvspace alii}}
\usepackage[authordate16,backend=biber,maxcitenames=2]{biblatex-chicago}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplemental material},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Supplemental material}
\author{}
\date{}

\begin{document}
\maketitle

\setstretch{2}
\appendix

\section{Coefficients, gain and phase shift functions}\label{sec-an-cof}

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{img/filters_used/lc.pdf}

@@

\end{figure}%

\centering{

\includegraphics[width=1\textwidth,height=\textheight]{img/filters_used/ql.pdf}
